Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-03-30 eg6-letters/long-paper/prc-dvcshelium.tex
edit figure 3, 12, 13 and adding the source files

\begin{figure}[tbp!]
\center
\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_coh_exc_cuts.pdf}
	\caption{Distributions of the coherent photon production events before 
	(black) and after (blue line filled
	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom. 
	}
\label{fig:CohExcCuts}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_incoh_exc_cuts.pdf}
\caption{Distributions of the incoherent photon production events before 
	(black) and after (blue line filled
	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
\label{fig:IncExcCuts}
\end{figure}

>>>>

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{fig3/all_coh_exc_cuts.png}
        \caption{Distributions of the coherent photon production events before 
        (blue) and after (black line filled
	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom. 
	}
\label{fig:CohExcCuts}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[trim=10 10 10 
   5,clip,width=16.5cm]{fig3/all_incoh_exc_cuts.png}
\caption{Distributions of the incoherent photon production events before (blue) 
   and after (black line filled
	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
	red dashed lines. The histograms are shown as a function of the 
	seven variables used for the exclusivity selection described in the text, 
	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
\label{fig:IncExcCuts}
\end{figure}
